---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README_files/README-"
)
```

[![Build Status](https://travis-ci.org/hrbrmstr/lineworkmaps.svg)](https://travis-ci.org/hrbrmstr/lineworkmaps) 
![Project Status: Concept - Minimal or no implementation has been done yet.](http://www.repostatus.org/badges/0.1.0/concept.svg)](http://www.repostatus.org/#concept)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/lineworkmaps)](http://cran.r-project.org/web/packages/lineworkmaps) 
![downloads](http://cranlogs.r-pkg.org/badges/grand-total/lineworkmaps)

lineworkmaps is ...

The following functions are implemented:

The following data sets are included:

### News

- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/lineworkmaps")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(lineworkmaps)
library(sp)
library(ggplot2)
library(ggthemes)

# current verison
packageVersion("lineworkmaps")

# plot admin1 polygons for Elmer Casual (the defaults)
plot(linework_map())

# plot the continental United States "Wargames" style
wargames <- linework_map("wargames", fortified=TRUE)

us <- wargames[wargames$iso_a2=="US" & 
               !wargames$code_hasc %in% c("US.HI", "US.AK"),]

ggplot(us) +
  geom_map(map=us, aes(x=long, y=lat, map_id=id)) +
  theme_map()

# fancier example just focusing on the U.S.
elmer <- linework_map("elmer_casual", fortified=TRUE)

us <- elmer[elmer$COUNTRY=="US" & 
            elmer$Name != "Alaska",]

gg <- ggplot()
gg <- gg + geom_map(data=us, map=us,
                    aes(x=long, y=lat, map_id=id),
                    color="#939598", fill="#d1d2d4", size=0.5)
gg <- gg + coord_map(project="albers", lat0=37.5, lat1=29.5)
gg <- gg + labs(title="Elmer Casual")
gg <- gg + theme_map()
gg <- gg + theme(plot.title=element_text(size=16))
gg

# info about the lineworks
lineworks(verbose=TRUE)
```

### Test Results

```{r}
library(lineworkmaps)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
