---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README_files/README-"
)
```

lineworkmaps is compilation of [Project Linework](http://projectlinework.org/) maps in `SpatialPolygonsDataFrame` and `ggplot2` fortified objects ready for mapping, et al.

I took a minimalist approach to the package in that I don't have every linework (the calligraphy one seemed less than useful) and the functions only work for Admin 0 & Admin 1 polygons.

Please file an issue if there is functionality you'd like to see that isn't included. The package is at a very early stage so almost no suggestion will be turned away!

To get an idea of what you can do with these lineworks in R, head on over to [RPubs](http://rpubs.com/hrbrmstr/project-linework). It has been updated to use this package. 

The Project Linework shapefiles also work well [with Leaflet](http://rpubs.com/hrbrmstr/linework-leaflet).

The following functions are implemented:

- `lineworks` : Return vector of available linework shapes and optionally print verbose description of shapfile data elements.
- `linework_map` :  Retrieve a linework map as a regular or fortified `SpatialPolygonsDataFrame`

The following data sets are included:

- `linework` : Project Linework spatial & fortified objects

### News

- Version 0.0.1.9001 : naming consistency
- Version 0.0.1.9000 : Added two new Project Linework map sets: Moriarty Hand and Weekend Update [[ref](http://www.projectlinework.org/2015/08/31/new_linework_sets.html)]
- Version 0.0.0.9000 released

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/lineworkmaps")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(lineworkmaps)
library(sp)
library(ggplot2)
library(ggthemes)

# current verison
packageVersion("lineworkmaps")

# plot admin1 polygons for Elmer Casual (the defaults)
plot(linework_map())

# plot the continental United States "Wargames" style
wargames <- linework_map("wargames", fortified=TRUE)

us <- wargames[wargames$iso_a2=="US" & 
               !wargames$code_hasc %in% c("US.HI", "US.AK"),]

ggplot(us) +
  geom_map(map=us, aes(x=long, y=lat, map_id=id)) +
  coord_map(project="albers", lat0=37.5, lat1=29.5) +
  theme_map()

# fancier example just focusing on the U.S.
elmer <- linework_map("elmer_casual", fortified=TRUE)

us <- elmer[elmer$COUNTRY=="US" & 
            elmer$Name != "Alaska",]

gg <- ggplot()
gg <- gg + geom_map(data=us, map=us,
                    aes(x=long, y=lat, map_id=id),
                    color="#939598", fill="#d1d2d4", size=0.5)
gg <- gg + coord_map(project="albers", lat0=37.5, lat1=29.5)
gg <- gg + labs(title="Elmer Casual")
gg <- gg + theme_map()
gg <- gg + theme(plot.title=element_text(size=16))
gg

# new maps: moriarty hand & weekend update

moriarty <- linework_map("moriarty_hand", fortified=TRUE)

us <- moriarty[substring(moriarty$ISO_3166_2, 1, 2) =="US" & 
               !(moriarty$ISO_3166_2 %in% c("US-AK", "US-HI")),]

gg <- ggplot()
gg <- gg + geom_map(data=us, map=us,
                    aes(x=long, y=lat, map_id=id),
                    color="#939598", fill="#d1d2d4", size=0.5)
gg <- gg + coord_map(project="albers", lat0=37.5, lat1=29.5)
gg <- gg + labs(title="Moriarty Hand Admin 1 CONUS")
gg <- gg + theme_map()
gg <- gg + theme(plot.title=element_text(size=16))
gg


moriarty <- linework_map("moriarty_hand", admin_level=0, fortified=FALSE)
moriarty <- subset(moriarty, region_un=="Africa")
moriarty <- fortify(moriarty)

gg <- ggplot()
gg <- gg + geom_map(data=moriarty, map=moriarty,
                    aes(x=long, y=lat, map_id=id),
                    color="#939598", fill="#d1d2d4", size=0.5)
gg <- gg + coord_quickmap()
gg <- gg + labs(title="Moriarty Hand Admin 0 - Africa")
gg <- gg + theme_map()
gg <- gg + theme(plot.title=element_text(size=16))
gg

weekend <- linework_map("weekend_update", admin_level=0, fortified=TRUE)
weekend <- subset(weekend, Country != "United States")

gg <- ggplot()
gg <- gg + geom_map(data=weekend, map=weekend,
                    aes(x=long, y=lat, map_id=id),
                    color="#939598", fill="#d1d2d4", size=0.5)
gg <- gg + coord_quickmap()
gg <- gg + labs(title="Weekend Update - Europe")
gg <- gg + theme_map()
gg <- gg + theme(plot.title=element_text(size=16))
gg

# info about the lineworks
lineworks(verbose=TRUE)
```

### Test Results

```{r}
library(lineworkmaps)
library(testthat)

date()

test_dir("tests/")
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
